\documentclass[0pt]{article}
\usepackage[margin=3cm]{geometry}
\usepackage{titling}
\setlength{\droptitle}{-10em} 
\title{Christopher Phillip Marriott}
\date{Home phone: 01455  440046; Mobile: 07528329448; E-mail: cpm4@aber.ac.uk}
\begin{document}
\maketitle
\thispagestyle{empty}
\pagestyle{empty}

\section*{Profile}
I am an enthusiastic hard working individual. I work well in and out of a group and love a challenge. I am currently in second year at Aberystwyth University studying Computer Science and expecting a first in my course.

\section*{Skills}
\begin{itemize}
	\item Knowledge in HTML, CSS, SQL, JavaScript, PHP, C, C++, VB, Python, Assembly, Java, Haskell, Perl, Microsoft Office, Libre Office, GitHub and 		LaTeX 
	\item Skilled with Linux and Windows
	\item Hardware installation experience
\end{itemize}

\section*{Employment History}
\subsection*{04/2009 -- 06/2011   Radio Shack, Hinckley -- Sales Assistant}
\begin{itemize}
	\item Trusted with key holding responsibilities
	\item Created and Maintained Database for orders and repairs
	\item Train staff members
	\item Handling money
	\item Advised on companies website
	\item Assisting customers with their enquiries
\end{itemize}
	
\subsection*{14/10/2008 for two weeks     Leicester University --  Data Input}
\begin{itemize}
	\item Entering data into an Access database
	\item Interpreting written data
\end{itemize}

\subsection*{11/2006 -- 06/2008      John Cleveland College -- Assistant Technician}
\begin{itemize}
	\item Examining computer labs for damaged or missing equipment
	\item Reporting problems back to the Head of ICT
	\item Fixing and replacing items
\end{itemize}

\section*{Education}
\subsection*{2011 -- 2015: Aberystwyth University}
\begin{tabbing}
~~~~~~~~~~~~~~~~~~~~~~~~\=\\
\> Computer Science 4 year (G401)\\
\\
\> Expected Outcome First\\
\\
\> Key Module: CS22120 Software Development Life Cycle   
\end{tabbing}

\subsection*{2003 -- 2008: John Cleveland College}  
\begin{tabbing}
\=~~~~~~~~~~~~~~~~~~~~~~~~\=\\
\> A Levels:  \>Computing \\

\>\>Psychology\\
\\
\> AS Levels: \>Physics \\
\\
\> GCSE Levels: \>English\\

\>\>Mathematics\\

\>\>Science\\

\>\>Computing\\

\>\>German\\
\end{tabbing}

\subsection*{Interests}
\begin{itemize}
	\item Fishing - Took up at a club I used to go where I came 2nd in their	 fishing competition.
	\item Archery - Took up at university after seeing it at the sports fair	.
	\item Building computer systems - Built first System in 2010 and have 		built and re-built 2 since then.
	\item Knitting - Taught by my Grandma in 2012 found it very fun and 		creative and have made a Scarf and Penguin since.
	\item Writing stories - I have have written a few short stories and am 		currently writing a longer one.
	\item Philosophy - General reading on philosophical ideas.
\end{itemize}

\subsection*{References}
Julie, Store Manager, Peacocks, Britannia Centre, Castle Street, Hinckley, Leicestershire, LE10 1RU, 
(01455) 234403
\\\\
Chris Howells, Owner, RadioShack, 81 Castle Street, Hinckley, Leicestershire, LE10 1DA,
(01455) 230808 

\end{document}















